---
title: "p8105_hw5_jl6048"
author: Jinghan Liu
output: github_document
---


```{r message=FALSE}
library(tidyverse)
library(readxl)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%")
```


## Problem 1

Imports and clean data
```{r}
homicide_df =
  read_csv("./data/homicide-data.csv", na = c("","Unknown")) %>%
  mutate(
        city_state = str_c(city, state),
        resolution = case_when(
           disposition == "Closed without arrest" ~"unsolved",
           disposition == "Open/No arrest" ~"unsolved",
           disposition == "Closed by arrest" ~"solved"
           ))%>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
homicide_df
```

Let's focus on Baltimore, MD

```{r}
baltimore_df =
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary =
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test =
prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n= baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```


Let's try to iterate across cities!
```{r}
prop_test_function = function(city_df){
  
  city_summary =
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n= n()
    )
  city_test =
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n))
  
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>%
  filter(city_state =="AlbuquerqueNM") %>%
  prop_test_function()

```

Now, let's iterate across all cities
```{r}
results_df =
  homicide_df %>%
  nest(data = uid:resolution)%>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  )%>%
  select(city_state,tidy_results)%>%
  unnest(tidy_results)%>%
  select(city_state,estimate, starts_with("conf"))
results_df
```


Try to make a plot showing estimates and confidence intervals.

```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state,estimate))%>%
  ggplot(aes(x = city_state,y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5,hjust =1))
  
```

```{r}
homicide_df %>%
  group_by(city_state)%>%
  summarize(
    unsolved = sum(resolution =="unsolved"),
    n = n()
  )%>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  )%>%
  select(city_state,tidy_results)%>%
  unnest(tidy_results)%>%
  select(city_state,estimate, starts_with("conf"))
```



## Problem 2

Read and Tidy data
```{r}
p2_df =
  tibble(
  files = list.files("./data/zip_data/"))%>% 
   mutate(
    path = str_c("data/zip_data/", files),
    data = map(path, read_csv)) %>% 
    unnest(data)%>% 
  mutate(id = str_remove(files, ".csv"),
         arm = case_when(str_detect(path, "con") ~ "control",
                         str_detect(path, "exp") ~ "experimental")) %>% 
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "observation") %>% 
  mutate(week = as.integer(str_replace(week, "week_",""))) %>% 
  select(id, arm, week, observation)

p2_df 
  
```

Make a spaghetti plot showing observations on each subject over time

```{r}
p2_df %>%
  
  ggplot(aes(x = week, y = observation, group = id, color = arm)) +
  geom_path() +
  labs(
    title = "Observations of Subjects Over 8 Weeks",
     x = "Week",
    y = "Observation value",
    caption = "Data from the longitudinal study"
  ) +
   viridis::scale_color_viridis(discrete = TRUE) + 
  theme(legend.position = "right")

```
**Comment**:
Obviously, the observation value of the experimental group of the study is higher than that of the control group.


## Problem 3

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r}
fill_in_missing  = function(x){
  
  if (is.numeric(x)){
    x = replace_na(x, mean(x, na.rm = TRUE))
  } 
  if (is.character(x)){
     x = replace_na(x, "virginica")
  }
  x
}

iris_cleaned = map(iris_with_missing, fill_in_missing) %>% 
  as_tibble() 
iris_cleaned

```

